Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2020-05-09 manuscript/manuscript.tex
updated new section

For small $t$, it is common to approximate $N_e$ as,

@@

Then, the drift-only $N_e$ (that is, removing the effects of linked selection)
replaces $V_T$ with $V_D$,

\begin{align}
  N_{e,D} &\approx \frac{t p_0(1-p_0)}{2 V_T(1 - G(t) - \varepsilon)} \\
          &\gtrsim  \frac{t p_0(1-p_0)}{2 V_T(1 - G(t))} \\
          &\gtrsim  \frac{N_e}{1 - G(t)}
\end{align}

>>>>

Under a Wright--Fisher population,

\begin{align}
  V_T = \var(p_t - p_0) = p_0(1 - p_0) \left[ 1 - (1 - \nicefrac{1}{2N_e})^t \right]
\end{align}

For small $t$, a common temporal estimator for the variance effective
population size $N_e$ is,

@@

Then, the drift-only $N_e$ estimate (that is, removing the effects of linked
selection) replaces the observable $V_T$ with unobservable $V_D$, and uses the
$G(t)$ estimate to bound this:

\begin{align}
  N_{e,D} &\approx \frac{t p_0(1-p_0)}{2 V_T(1 - G(t) - \varepsilon)} \\
          &\gtrsim  \frac{t p_0(1-p_0)}{2 V_T(1 - G(t))} \\
          &\gtrsim  \frac{N_e}{1 - G(t)} \\
  \frac{N_e}{N_{e,D}} &\lesssim  1 - G(t)
\end{align}
